Optimizing Path ORAM for Cloud Storage Applications

### 2014-11-30 paper/paper.tex
Update paper.tex

\label{sec:BlkPack}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=4.3cm]{550.pdf}\includegraphics[width=4.3cm]{551.pdf}
\caption{Block Packing evaluations comparing tree size (in nodes) and throughput (in MB/sec)  with various file sizes (at segment size of 4 KB.)}
\label{fig:blockpack}
\end{center}
\end{figure}

@@

\section{Future Work}

In the future we plan to more fully detail the merits and deficits of our Path ORAM implementation through additional tests and, where needed, further optimizations. We believe that this will allow us to grow our project into a full-fledged software package.

One additional optimization is to implement a “hybrid” ORAM system. This would combine the current Path system when using small files with a scan system, which is much more efficient for large files. We have also determined ways to optimize the stash algorithm, which we could implement in our system as well.

Our final goal for this project is to make it into a public software package. This would require several additions, including a better user interface and crash recovery solutions. Crash recovery poses a major obstacle to implementation; without a recovery mechanism, a crash in the middle of syncing with Dropbox could result in lost data.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.

@@

>>>>

\label{sec:BlkPack}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=4.3cm]{550.pdf}\includegraphics[width=4.3cm]{551.pdf}
\caption{Block Packing evaluations comparing tree size (in nodes) and throughput (in MB/sec) with various file sizes. }
\label{fig:blockpack}
\end{center}
\end{figure}

@@

@@

In the future we plan to make our work into a public full-fledged software package, with a crash recovery mechanism and possibly other optimizations.
